Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-19 paper/v2.0/sections/1_introduction.tex
Add new citations

Manipulating light-matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the last century. Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21,wijesekara21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, and quantum cavity physics \cite{tsang10,devi20}.
However, in recent years, one of the foremost aim of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.

>>>>

Manipulating light-matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the last century. Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21,wijesekara21}, sensing \cite{rodrigo15,pirandola18,hapuarachchi2018}, energy harvesting \cite{weeraddana15,yuan16,sun18},
quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{chow13,jayasekara16,premaratne17}, and quantum cavity physics \cite{tsang10,liu17,devi20}.
However, in recent years, one of the foremost aim of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
